Appendix

### 2019-07-16 manuscript/appendix.Rmd
recolor

```{r trophic_state, fig.cap="Lake trophic state", fig.width = 6, fig.height = 3.2, warning=FALSE, message=FALSE}
lg <- lagosne_load("1.087.1")
focal_hu4s <- data.frame(hu4_zoneid = paste0("HU4_", 
                                             c("56", "57", "36", "37", "38")), 
                         stringsAsFactors = FALSE)

@@

# g <- gridExtra::tableGrob(dt, rows = rep("", nrow(dt)))
# grid.draw(g)

# waffle
library(waffle)
library(hrbrthemes)

@@

ggplot(dt_waffle,
       aes(fill=`Trophic State`, values = `value`)) +
  geom_waffle(color = "white", size=0.7, n_rows = 5) +
  facet_wrap(~key, ncol=1) +
  scale_x_discrete(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0)) +
  ggthemes::scale_fill_tableau(name=NULL) +
  coord_equal() +
  labs(title = "Trophic State")  +
#   theme_ipsum_rc(grid="") +
   theme_enhance_waffle() + 
  theme(strip.background = element_blank(), 
        rect = element_rect(fill = "transparent"), 
        legend.position = "bottom", 
        title = element_text(size = 18), 
        strip.text = element_text(size = 16), 
        legend.text = element_text(size = 10), 
        legend.key.size = unit(0.5, "line")) + 
  guides(fill = guide_legend(nrow = 2))

>>>>

```{r data_prep, fig.cap="Lake trophic state", fig.width = 6, fig.height = 3.2, warning=FALSE, message=FALSE}
lg <- lagosne_load("1.087.1")
focal_hu4s <- data.frame(hu4_zoneid = paste0("HU4_", 
                                             c("56", "57", "36", "37", "38")), 
                         stringsAsFactors = FALSE)

@@

# g <- gridExtra::tableGrob(dt, rows = rep("", nrow(dt)))
# grid.draw(g)
```

```{r trophic_state, fig.cap="Lake trophic state", fig.width = 6, fig.height = 3.2, warning=FALSE, message=FALSE}
# waffle
library(waffle)
library(hrbrthemes)

@@

ggplot(dt_waffle,
       aes(fill=`Trophic State`, values = `value`)) +
  geom_waffle(color = "white", size=0.7, n_rows = 5) +
  facet_wrap(~key, ncol = 1) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
                    shades::delta(-10)) +
  coord_equal() +
  theme_enhance_waffle() + 
  theme(strip.background = element_blank(), 
        rect = element_rect(fill = "transparent"), 
        legend.position = "bottom", 
        title = element_blank(), 
        strip.text = element_text(size = 16), 
        legend.text = element_text(size = 10), 
        legend.key.size = unit(0.5, "line")) + 
  guides(fill = guide_legend(nrow = 2))
